\chapter*{Abstract}

Using computer vision algorithms to track objects in variable three-dimensional environments and using the found poses to guide complex construction tasks is an interesting area of research which opens up a lot of exciting possibilities. If the construction is performed by a human using a mixed reality headset promises great flexibility an easy of use.

In this thesis I integrate a preexisting object tracking library into the HoloLens 2 ecosystem and build a small application with a simple user interface. This application enables the user to use object tracking to accurately build a simple brick tower by hand. To accomplish this, I make use of various Windows APIs and the new Research Mode for HoloLens 2 to provide the Object Tracker with the data streams it needs.

\cleardoublepage
\chapter*{Zusammenfassung}

Das Tracking von Objekten in variablen drei-dimensionalen Umgebungen zur Unterstützung von Bauvorhaben von komplexen Konstruktionen ist ein aktives Forschungsgebiet, welches viele spannende Möglichkeiten bietet. Für Fälle, wo die Konstruktion von einem Menschen per Hand ausgeführt wird, ist es für die höchstmögliche Flexibilität vielversprechend, ein  Mixed-Reality Headset einzusetzen.

In dieser Arbeit integriere ich eine bereits existierende Objekt-Tracking Library in das Ökosystem der HoloLens 2 und baue eine kleine Applikation mit einem einfachen User Interface. Diese Applikation kann genutzt werden, um einen kleinen Turm aus Bauklötzen mit grosser Präzision per Hand zu konstruieren. Um dieses Zeil zu erreichen verwende ich verschiedene Windows APIs und den neuen Research Mode für die HoloLens 2, um den Objekt-Tracker mit den nötigen Datenströmen zu versorgen.
